Deep Learning for Automatic Speech Recognition

### 2015-04-29 Paper/Paper.tex
Helps to include the .tex file

% packages for doing elaborate table stuff
\usepackage{array}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tabularx}
% Used to have a table span multiple pages.
\usepackage{longtable}

@@

@@

\paragraph{} In this section we discuss the work on Large-Vocabulary Speech Recognition (LVSR) of \cite{DBLP:journals/taslp/DahlYDA12} consisting of a context dependent hidden Markov model and deep neural network hybrid architecture (CD-HMM-DNN) for the acoustic model. We will begin with an overview of the general architecture, then explain the algorithms used for pre-training, and conclude with a discussion on the general procedure for training. Discussion of experimental results for this approach are deferred to the results section so that they can be compared to the convolutional neural network approach.

@@

\paragraph{} Based on this formalism, \cite{DBLP:journals/taslp/DahlYDA12} chose to use pre-trained deep neural networks to estimate $\cprob{q_t}{x_t}$ using MFCCs as DNN inputs and taking the senone posterior probabilities as DNN outputs. The transitioning between events is best modeled by hidden markov model whose notation, $\pi, a$, and $q$ appears in Eqn. (\ref{eqn:lm:def}). Now that we have an overview of the general CD-DNN-HMM architecture, we can look at how \cite{DBLP:journals/taslp/DahlYDA12} train their model.

@@

\paragraph{} To understand the pre-training process, it is necessary to discuss Restricted Boltzmann Machines (RBM) and Deep Belief Networks (DBN). RBMs are an undirected bipartite graphical model with Gaussian distributed input nodes in a visible layer connecting to binary nodes in a hidden layer. Every possible arrangement of hidden, $h$, and visible, $v$, nodes is given an energy under the RBM model:

@@

Where $\sigma$ is an element wise logistic function. \cite{DBLP:journals/taslp/DahlYDA12} argue that Eq. (\ref{eqn:dahlEq7}) allows one to repurpose the RBM parameters to initialize a neural network. Training of the RBM is done by stochastic gradient descent against the negative log likelihood since we wish to find a stable energy configuration for the model:

@@

\paragraph{} Now that we have an understanding of RBMs, we can shift our focus to DBNs. Deep Belief Networks are multilayer models with undirected connections between the top two layers and directed between other layers. To train these models, \cite{DBLP:journals/neco/HintonOT06} had the insight to treat adjacent layers of nodes as RBMs. One starts with the bottom two layers and trains them as though they were a single RBMS. Once those two layers are trained, then that top layer of he RBM is treated as the input layer of a new RBM with the layer above that layer acting is the hidden layer of the new RBMs. The sliding window over the layers continues until the full DBN is trained.  After this, \cite{DBLP:journals/neco/HintonOT06} describe an "up-down" algorithm to further refine the learned weights. The learned parameters of this greedy approach can then be used as the parameters of a DNN as explained earlier.

@@

\begin{table}[H]
	\centering
	\begin{tabular}{c|c|c|c}
		& Switchboard & Bing Mobile & TIMIT \\
		& (WER) & (SER) & (PER) \\
		\hline
		GMM & 23.6 \textsuperscript{[2]} & 36.2 \textsuperscript{[1]} & 21.7 \textsuperscript{[2]} \\
		DNN & 16.1 \textsuperscript{[2]} & 30.4 \textsuperscript{[1]} & 21.9 \textsuperscript{[3]} \\
		CNN & $-$ & $-$ & 20.2 \textsuperscript{[3]} \\
		\hline
		RNN & $-$ & $-$ & 17.7 \textsuperscript{[4]}
	\end{tabular}
	\caption{Comparison of different architectures on different datasets and their corresponding datasets as reported from the following sources: [1] \cite{DBLP:journals/taslp/DahlYDA12}, [2] \cite{DBLP:journals/spm/X12a}, [3] \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, [4] \cite{DBLP:conf/icassp/GravesMH13}. }
	\label{tbl:results}
\end{table}

\paragraph{} Direct comparison of system is complicated by the variety of error metrics and datasets; we rely on \cite{DBLP:journals/spm/X12a} to fill in some gaps between our two selected papers to make a meaningful comparison. As one can see, the neural network approaches do better on average over the traditional GMM approach. To illustrate that it is not only DNN and CNN approaches that do better, we include the work of \cite{DBLP:conf/icassp/GravesMH13} on Recurrent Neural Networks (RNN) to further drive the point that general neural network architectures are viable alternatives to GMMs.

@@

\paragraph{} In \cite{DBLP:journals/spm/X12a}, the authors of both research groups suggest key gains will come from improved understanding of the pre-training process and how the types of units used in these models affect error rates. They conclude that distributed training is the largest hurdle to overcome for these systems so that more training data can be used efficiently. (Parallelization is limited by the sequential stochastic gradient descent at the heart of the pre-training and training processes.) As \cite{DBLP:journals/taslp/DahlYDA12} point out in their paper, GPU-based approaches can assist in reducing computation time, but more foundational approaches need to be pursued.

>>>>

% packages for doing elaborate table stuff
\usepackage{array}

%http://tex.stackexchange.com/questions/12703/how-to-create-fixed-width-table-columns-with-text-raggedright-centered-raggedlef
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage{multicol}
\usepackage{multirow}
\usepackage{tabularx}
% Used to have a table span multiple pages.
\usepackage{longtable}

@@

\newcommand{\CNN}{Convolutional Neural Network\xspace}
\newcommand{\DBN}{Deep Belief Network\xspace}
\newcommand{\DNN}{Deep Neural Network\xspace}
\newcommand{\GMM}{Gaussian Mixture Model\xspace}
\newcommand{\HMM}{Hidden Markov Model\xspace}
\newcommand{\RBM}{Restricted Boltzmann Machine\xspace}
\newcommand{\RNN}{Recurrent Neural Network\xspace}

@@

\paragraph{} In this section we discuss the work on Large-Vocabulary Speech Recognition (LVSR) of \cite{DBLP:journals/taslp/DahlYDA12} consisting of a context dependent \HMM and \DNN hybrid architecture (CD-HMM-DNN) for the acoustic model. We will begin with an overview of the general architecture, then explain the algorithms used for pre-training, and conclude with a discussion on the general procedure for training. Discussion of experimental results for this approach are deferred to the results section so that they can be compared to the \CNN approach.

@@

\paragraph{} Based on this formalism, \cite{DBLP:journals/taslp/DahlYDA12} chose to use a pre-trained \DNN to estimate $\cprob{q_t}{x_t}$ using MFCCs as DNN inputs and taking the senone posterior probabilities as DNN outputs. The transitioning between events is best modeled by hidden markov model whose notation, $\pi, a$, and $q$ appears in Eqn. (\ref{eqn:lm:def}). Now that we have an overview of the general CD-DNN-HMM architecture, we can look at how \cite{DBLP:journals/taslp/DahlYDA12} train their model.

@@

\paragraph{} To understand the pre-training process, it is necessary to discuss the \RBM (RBM) and \DBN (DBN) models. RBMs are an undirected bipartite graphical model with Gaussian distributed input nodes in a visible layer connecting to binary nodes in a hidden layer. Every possible arrangement of hidden, $h$, and visible, $v$, nodes is given an energy under the RBM model:

@@

Where $\sigma$ is an element-wise logistic function. \cite{DBLP:journals/taslp/DahlYDA12} argue that Eq. (\ref{eqn:dahlEq7}) allows one to repurpose the RBM parameters to initialize a neural network. Training of the RBM is done by stochastic gradient descent against the negative log likelihood since we wish to find a stable energy configuration for the model:

@@

\paragraph{} Now that we have an understanding of RBMs, we can shift our focus to DBNs. A \DBN is a multilayer model with undirected connections between the top two layers and directed between other layers. To train these models, \cite{DBLP:journals/neco/HintonOT06} had the insight to treat adjacent layers of nodes as RBMs. One starts with the bottom two layers and trains them as though they were a single RBM. Once those two layers are trained, then the top layer of the RBM is treated as the input layer of a new RBM with the layer above that layer acting as the hidden layer of the new RBM. The sliding window over the layers continues until the full DBN is trained.  After this, \cite{DBLP:journals/neco/HintonOT06} describe an "up-down" algorithm to further refine the learned weights. The learned parameters of this greedy approach can then be used as the parameters of a DNN as explained earlier.

@@

\begin{table}[H]
	\centering
	\begin{tabular}{c|C{1in}|C{1in}|C{1in}}
		& Switchboard & BMVS & TIMIT \\
		& (WER) & (SER) & (PER) \\
		\hline
		GMM & 23.6 \textsuperscript{[2]} & 36.2 \textsuperscript{[1]} & 21.7 \textsuperscript{[2]} \\
		DNN & 16.1 \textsuperscript{[2]} & 30.4 \textsuperscript{[1]} & 21.9 \textsuperscript{[3]} \\
		CNN & $-$ & $-$ & 20.2 \textsuperscript{[3]} \\
		\hline
		RNN & $-$ & $-$ & 17.7 \textsuperscript{[4]}
	\end{tabular}
	\caption{Comparison of different architectures on different datasets and their corresponding datasets as reported from the following sources: [1] \cite{DBLP:journals/taslp/DahlYDA12}, [2] \cite{DBLP:journals/spm/X12a}, [3] \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, [4] \cite{DBLP:conf/icassp/GravesMH13}. }
	\label{tbl:results}
\end{table}

\paragraph{} Direct comparison of system is complicated by the variety of error metrics and datasets; we rely on \cite{DBLP:journals/spm/X12a} to fill in some gaps between our two selected papers to make a meaningful comparison. As one can see from Table (\ref{tbl:results}), the neural network approaches do better on average over the traditional GMM approach. To illustrate that it is not only DNN and CNN approaches that do better, we include the work of \cite{DBLP:conf/icassp/GravesMH13} using a \RNN (RNN) to further drive the point that general neural network architectures are viable alternatives to GMMs.

@@

\paragraph{} In \cite{DBLP:journals/spm/X12a}, the authors of both research groups suggest key gains will come from improved understanding of the pre-training process and how the types of units used in these models affect error rates. They conclude that distributed training is the largest hurdle to overcome for these systems to make use of more training data. (Parallelization is limited by the sequential stochastic gradient descent at the heart of the pre-training and training processes.) As \cite{DBLP:journals/taslp/DahlYDA12} point out in their paper, GPU-based approaches can assist in reducing computation time, but more foundational approaches need to be pursued.
